On Secure Delegation of SampBQP with a Classical Client

### 2020-02-28 bqp.tex
Work on BQP intros

In this section we build our constant-round blind delegation protocols for $\BQP$ and $\FBQP$ with classical clients.
We first construct our protocol for $\BQP$ in \cref{subsec:BlindBQP}, then use it to construct our protocol for $\FBQP$ in \cref{subsec:BlindFBQP}.

@@

We build our constant-round blind delegation protocol for $\BQP$ first.
We start with the protocol for $\BQP$ from \cite{mf16}, where the verifier requires a single-qubit register and is classical otherwise.
We first obtain blindness by running said protocol under the homomorphic encryption given in \cite{mahadev_qfhe}.
We then make the verifier fully classical using the same argument as used in \cite{FOCS:Mahadev18a}.
Lastly, we use analysis from \cite{parallelrep, alagic2019twomessage} to ensure that it has negligible completeness and soundness errors while still being constant-round.

@@

\begin{thm}
	\label{thm:BlindBQP}
	$\Piblind$ has negligible completeness and soundness, and is blind.
\end{thm}
\begin{prf}
	The completeness follows by inspection.
	For blindness, the only thing the prover receives is $c$ and $pk$, so it follows directly from $\mathsf{QHE}$'s security.

@@

	We now prove that $\PMFstar$ in fact violates the soundness of $\PiMF$.
	Let $\cP_\blind^*$ denote the action $\Pblindstar$ takes to produce $\sigma$ from $ct_x$.
	Observe that the experiments $(\PMFstar, \VMF)(x)$ and $(\Pblindstar, \Vblind(x))$ are identical except for how $w$ is obtained from $\sigma$.
	so by \cref{decodeMeasureOrder} they are equivalent.
	Hence we have $\PMFstar$ with noticeable acceptance probability $\varepsilon$, which is a contradiction.
\end{prf}

@@

Next, we make the verifier completely classical by using \protoref{urmila4} from \cite{FOCS:Mahadev18a}.
It was originally used to compile $\PiMF$ into $\PiMFZ$ that is $\QPIP_0$. \Ethan{Say a bit more?}
It can however be applied to any $\QPIP_1$ protocol with $X$ and $Z$ measurement and negligible completeness and soundness errors.

@@

\begin{thm}
	$\Pibz$ has negligible completeness error. Its soundness error is negligibly close to $\frac{3}{4}$. It is blind.
\end{thm}
\begin{prf}
	Theorem $8.6$ in \cite{FOCS:Mahadev18a} compiles $\PiMF$ into a $\QPIP_0$ in a similar way and obtains this completeness and soundness.
	Its proof uses only that $\PiMF$ is $\QPIP_1$ with only $X$ and $Z$ measurements on the verifier's side, with negligible completeness and soundness errors.
	So the same argument applies here. \Ethan{TODO proofread me}

@@

Again, the same argument from \cref{thm:MFZrep} applies. We simply repeat $\Pibz$ in parallel to get $\Pibzrep$.

@@

Here we construct our delegation protocol for $\FBQP$.
The idea is to break any $\FBQP$ instance down into $\BQP$ instances by considering the output bit-by-bit,
so we can apply our results for $\BQP$.

@@

	Public input: $f$

>>>>

In this section we build our constant-round blind delegation \Ethan{Does ``delegation" imply verifiable?} protocols for $\BQP$ and $\FBQP$ with classical clients.

In \cref{subsec:BlindBQP} we start with the protocol for $\BQP$ from \cite{mf16}.
It has negligible completeness and soundness errors, but is not blind.
Its verifier requires a single-qubit register and is classical otherwise.
We first achieve blindness by running said protocol under the homomorphic encryption given in \cite{mahadev_qfhe}.
We then make the verifier fully classical by using the compiler used in \cite{FOCS:Mahadev18a} even though it deteriorates soundness.
Finally, we recover soundness while maintaining constant-round by running multiple copies in parallel,
which we analyze using \cite{parallelrep, alagic2019twomessage}.

In \cref{subsec:BlindFBQP} we then construct our protocol for $\FBQP$.
The idea is to break any $\FBQP$ instance down into $\BQP$ instances by considering the output bit-by-bit,
so we can apply our results for $\BQP$.

@@

@@

\begin{thm}
	\label{thm:BlindBQP}
	$\Piblind$ has negligible completeness and soundness, and is blind.
\end{thm}
\begin{prf}
	The completeness follows by inspection.
	For blindness, the prover receives only $ct_x$ and $pk$, so it follows directly from $\mathsf{QHE}$'s security.

@@

	We now prove that $\PMFstar$ in fact violates the soundness of $\PiMF$.
	Observe that the experiments $(\PMFstar, \VMF)(x)$ and $(\Pblindstar, \Vblind(x))$ are identical except for how $w$ is obtained from $\sigma$,
	so by \cref{decodeMeasureOrder} they are equivalent.
	Hence we have $\PMFstar$ with noticeable acceptance probability $\varepsilon$, which is a contradiction.
\end{prf}

@@

Next, we make the verifier completely classical by compiling $\Piblind$ using \protoref{urmila4} from \cite{FOCS:Mahadev18a}.
It was originally used to compile $\PiMF$ into $\PiMFZ$,
but in fact can be applied to any $\QPIP_1$ protocol to achieve similar effects.

@@

\begin{thm}
	$\Pibz$ has negligible completeness error. Its soundness error is negligibly close to $\frac{3}{4}$. It is blind.
\end{thm}
\begin{prf}
	Theorem $8.6$ in \cite{FOCS:Mahadev18a} compiles $\PiMF$ into a $\PiMFZ$ which is $\QPIP_0$ in a similar way and obtains this completeness and soundness.
	Its proof uses only that $\PiMF$ is $\QPIP_1$ with only $X$ and $Z$ measurements \Ethan{phrasing}, with negligible completeness and soundness errors.
	So the same argument applies here. \Ethan{TODO proofread me? Does 2-round vs 1-round matter?}

@@

The argument from \cref{thm:MFZrep} applies here too. We simply repeat $\Pibz$ for $\poly(n)$ times in parallel to get $\Pibzrep$.

@@

Here we state our delegation protocol for $\FBQP$.
\Ethan{TODO high level overview, and mention one-sided vs two-sided}

@@
